---
title: "Getting Started with Binomial"
author: "Youngjun Woo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(binomial)
```

## Binomial

The package `"Binomial"` is implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## bin_choose(n, k)

In order to calculate the probability of binomial distribution of given trials, probability, and success, we have to calculate the number of combinations in which k success can occur in n trials.
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

## bin_probability(success, trials, prob)

We can get calculated probability from binomial distribution when we are given success, trials, and prob.
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)

bin_probability(success = 0:2, trials = 5, prob = 0.5)

bin_probability(success = 55, trials = 100, prob = 0.45)
```

## bin_distribution(trials, prob)

We can get data frame with the binomial probability distribution: success in the first column, probability in the second column.
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

The `plot()` function gives us a barplot to display the probability histogram of a binomial distribution.
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## bin_cumulative()

We can get data frame with both the probability distribution and the cummulative probabilities: successes in the fist column, probability in the second column, and cumulative in the third column.
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

The `plot()` function gives us a graph to display the cumulative distribution.
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## bin_variable()

This function check numbers of input trials and probability and shows input trials and prob.
```{r}
bin_variable(trials = 10, p = 0.3)
```

The `summary()` function gives us a nice table of related statistics of binomial distribution.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

